Followers Are Not Enough: Beyond Structural Communities in Online Social Networks \\Followers Are Not Enough: A Question-Oriented Approach to Community Detection

### 2014-07-30 paper-for_arxiv/results.tex
new figure for comm sizes
starting conc

\begin{figure}[ht]
  \centering
\includegraphics[width=0.50\textwidth]{comm_sizes_ecdf_loglog.pdf}
\caption{The proportion of communities greater than $s$ in size, across the different community types. Note the logarithmic scale on the horizontal and vertical axes.}
\label{Fig-community_size_distribution}
\end{figure}

@@

Another interesting example is a community whose topics tend to focus on Denver and Colorado. These users do not belong to the same community in the interaction-based network, but most of them do belong to the same community in the activity-based network. This indicates that these users react to the same events and issues regarding Colorado and are therefore strongly connected in the topic-based and activity-based networks, but at the same time they do not directly interact with each other and are therefore more loosely connected in the interaction-based networks, where they belong to different communities. As expected, among the most influential users (in terms of transfer entropy) we find \@Colorado, which is the state official Twitter account, \@ConnectColorado, a page created to connect Coloradans, and CBS Denver account.

>>>>

\begin{figure}[ht]
  \centering
%\includegraphics[width=0.50\textwidth]{comm_sizes_ecdf_loglog.pdf}
\includegraphics[width=0.6\textwidth,angle=270]{cdf_comm_sizes.eps}
\caption{The proportion of communities greater than $s$ in size, across the different community types. Note the logarithmic scale on the horizontal and vertical axes.}
\label{Fig-community_size_distribution}
\end{figure}

@@

\alert{work from here after Crossfit}
Another interesting example is a community whose topics tend to focus on Denver and Colorado. These users do not belong to the same community in the interaction-based network, but most of them do belong to the same community in the activity-based network. This indicates that these users react to the same events and issues regarding Colorado and are therefore strongly connected in the topic-based and activity-based networks, but at the same time they do not directly interact with each other and are therefore more loosely connected in the interaction-based networks, where they belong to different communities. As expected, among the most influential users (in terms of transfer entropy) we find \@Colorado, which is the state official Twitter account, \@ConnectColorado, a page created to connect Coloradans, and CBS Denver account.
